\begin{multicols}{2}
\section{APPENDIX 3 {-} YOUR COMMITMENTS}

\subsection{In addition to provisions of the Agreement the Client also agree to:}

\begin{enumerate}
	\item	During the Heating Season windows of the Apartments in the
		Building may be opened only in cases stipulated in the Agreement in line with
		the procedure established by the Agreement.
	\item   During the Heating Season the windows of the Apartments in the
		Building may be opened for no more than [X] minutes in 24 hours to ensure
		circulation of air, if:
	\begin{enumerate}
		\item	strong smell of cleaning products persists in the Apartment;
		\item	strong smell of cooking persists in the Apartment;
		\item	during cleaning or the apartment and/or after cleaning of the apartment it is necessary to get rid of dust.
	\end{enumerate}
	\item	During the Heating Season windows in the Apartments of the
		Building may be opened at any time, if it is necessary for health of a person
		staying in the Apartment.
	\item	During the Heating Season windows of the common areas of the
		Building, especially windows of stairways, have to be kept closed.
	\item	The Client shall procure that all entrance doors of the Building are kept closed during the Heating Season.
	\item	The Client shall procure that all common areas of the Building
		which the Contractor has renovated for the sake of energy efficiency
		improvement or esthetical considerations are clean and comply with generally
		acceptable standards of the general public about health, hygiene and order.
	\item	In case of renovation of the Apartment the Client shall inform
		the Contractor about the timeline when such reconstruction might affect energy
		consumption at the Building, including but not limited to cases when one or
		more of the below listed measures are planned:
	\begin{enumerate}
		\item	replacement of the thermal convector and/or heating element;
		\item	replacement of windows;
		\item	extension of the Billing Area including space of the balcony;
		\item	installation of mechanical ventilation systems.
	\end{enumerate}
\end{enumerate}

In cases referred to in this clause the Contractor is entitled to revise the energy Baseline established in the Agreement.

\end{multicols}
