\section{APPENDIX 1 {-} DEFINITIONS}
The Parties agree for the purposes of this Agreement that the definitions below shall have the following meaning:

\begin{center}
\begin{longtabu}{|X|X[3]|}  \hline{}
	Agreement & This energy performance contract concluded between the Client and the Contractor including its Annexes and General Terms and conditions. \\ \hline{}
	Apartment & Every apartment property located in the Building for the purpose of the laws and regulations. \\ \hline{}
	Apartment Owner & An individual or a legal entity in whose name the
			  Apartment is recorded with the Land Register, or another person who pursuant to
			  laws and regulations holds the property title over the respective Apartment or
			  to whom the property title of the respective Apartment Owner is transferred to
			  whether under the provisions of the law or pursuant to a contractual
			  arrangement. \\ \hline{}
	Baseline & The Baseline represents the conditions of the building
		   before the implementation of Renovation Works and includes the base year
		   measured energy data and base year conditions of the building. \\ \hline{}
	Baseyear energy data & The measured energy consumption during the years
			       selected for the baseline and representative of the building energy performance
			       before the implementation of Renovation Works. \\ \hline{}
	Baseyear conditions & The set of conditions which gave rise to the
			      energy use/demand of the base year, in particular indoor air temperature,
			      outdoor air temperature, length of the heating seasons. \\ \hline{}
	Billing area & Billing Area is the area of the Building being inhabited
		       by residents, including the total area of the Apartments without balconies,
		       terraces, porticos, loggias or such others as indicated and agreed upon in
		       Annex No. 3 to the Agreement. \\ \hline{}
	Building & Multi{-}apartment residential building at [address]. \\ \hline{}
	Business day & An official working day that is not pronounced as an official holiday or an official work day off as determined under Latvian law. \\ \hline{}
	Comfort Standarts & The required minimum level of comfort as set out in Annex No 2 (“Comfort Standards”) to the Agreement \\ \hline{}
	Commencement Date & The date on which the renovation works and the
			    implementation of the Renovation Works are expected to be initiated by the
			    Contractor. The Contractor will inform the Client of the provisional
			    Commencement Date, not later than within 30 days after the signing of this
			    Agreement. \\ \hline{}
	Confidential Information & The term "Confidential Information", as used
				   in this Agreement, includes any data or information, whether in tangible or
				   intangible form, that is proprietary to a Party (“Disclosing Party”) or has
				   been acquired or disclosed by third parties (whether under a non{-}disclosure
				   agreement or otherwise) whenever and however disclosed to the other Party (the
				   “Receiving Party”), including, but not limited to:
				   \begin{itemize}
					\item	any marketing strategies,
						plans, financial information, business plans and performance results relating
						to the past, present or future business activities of the Disclosing Party, its
						Clients, partnering organizations, its affiliates, subsidiaries or otherwise
						affiliated entities;
					\item	plans for products or services, and supplier lists;
					\item	any scientific or technical
						information, inventions, designs, process, procedure, formula, improvement,
						technology or method disclosed by the Disclosing Party, irrespective of whether
						proprietary or not to the Disclosing Party or its partnering organizations in
						the Project;
					\item	any concepts, reports, data,
						know{-}how, works-in-progress, designs, development tools, drawings,
						specifications, flow charts, databases, inventions, patents and trade secrets;
						and
					\item	any other information that
						should reasonably be recognized as confidential information of the Disclosing
						Party, its partnering organizations, companies associated for the purposes of
						this Agreement, subsidiaries, affiliates or otherwise related companies,
						including information of personal nature or information relating to the private
						life of any of the Apartment Owners.
						Confidential Information need not be novel, unique, patentable, copyrightable
						or constitute a trade secret in order to be designated as Confidential Information.
					\end{itemize} \\ \hline{}
	Construction Period & The period required for the installation, putting
			      into operation and testing of the Facilities at the Building. The Construction
			      Period is provisionally estimated to last for [X], which period shall be
			      considered to start to run from the Commencement Date unless the Commencement
			      Date is postponed pursuant to the provisions of this Agreement. \\ \hline{}
	Degree Day & A degree day is the measure of the heating load on a
		     building created by outdoor temperature. When the mean daily outdoor
		     temperature is one degree below the indoor temperature, for one day, it is
		     defined that there is one heating degree day. If this temperature difference
		     prevailed for ten days there would be ten heating degree days counted for the
		     total period. If the temperature difference were to be 12 degrees for 10 days,
		     120 heating degree days would be counted. When the ambient temperature is below
		     the reference temperature it is defined that heating degree days are counted. \\ \hline{}
	Delivery and acceptance of the Facilities & Upon completion of the implementation of the agreed hereunder Renovation Works
						    in the Building, the representative of the Client shall be invited for the delivery
						    and acceptance of the Facilities. The Client’s and the Contractor’s representatives shall sign
						    a bilateral protocol evidencing the executed work and depicting in details
						    (including via photo material) the conditions in which the Facilities are being
						    handed over to the possession of the Client.
						    If the Client has not provided a representative with the corresponding power of
						    attorney within the period of 5 (five) days from the receipt of the respective
						    notice from the Contractor, it shall be held that the Facilities have been
						    delivered and accepted by the Client in the manner prescribed in the protocol
						    signed by the Contractor alone.
						    Any claims or complains against the quality or execution manner for any part of
						    the Contractor’s work shall be considered as waived in case not filed via
						    e{-}mail within 5 (five) Business days as of the signing of the bilateral
						    protocol evidencing passing over of the possession of the Facilities to the Client.	\\ \hline{}
	EMS (Energy Management System) & Energy management system means a set
					 of interrelated or interacting elements of a plan which sets an energy
					 efficiency objective and a strategy to achieve that objective \\ \hline{}
	Energy & Energy means all forms of energy products, combustible fuels,
		 heat, renewable energy, electricity, or any other form of energy required for
		 heating of the Building and heating of domestic hot water consumed with a view
		 to achieving the Comfort Standards established in the Agreement. \\ \hline{}
	Energy Audit & A systematic procedure with the purpose of obtaining
		       adequate knowledge of the existing conditions and energy consumption profile of
		       a Building or installation, identifying and quantifying cost{-}effective energy
		       savings opportunities, and reporting the findings. \\ \hline{}
	Energy Efficiency & Means the ratio of output of performance, service, goods or energy, to input of energy. \\ \hline{}
	Energy Savings & Means the amount of saved energy determined by
			 measuring and/or estimating consumption before and after implementation of the
			 Renovation Works, whilst ensuring normalisation for external conditions that
			 affect energy consumption. \\ \hline{}
	Energy Tariff & Charge for Energy unit measured in MWh and as set out
			by an Energy Supplier where the building is located, which is valid during the
			certain period of time and which is approved by the applicable
			Regulator/Agreement. \\ \hline{}
	Guaranteed Energy Consumption & The guaranteed amount of [X] MWh of
					energy to be consumed after implementation of the Renovation Works which
					represents a [X] \% increase in the energy efficiency performance of the
					Building compared to its Baseline. For the purposes of avoiding doubt, the
					Contractor guarantees that the adjusted energy consumption of the Building
					after the Renovation Works shall not be above its guaranteed energy consumption
					amounts and separately undertakes to exercise additional reasonable in terms of
					costs efforts to further decrease the energy consumption for the entire
					duration of this Agreement. \\ \hline{}
	Facilities & Material, equipment, systems, fittings and other measures
		     installed by the Contractor or otherwise invested in the Building as part of
		     the Renovation Works or for the Measurement and Verification, , maintenance and
		     repair thereof, in accordance with the Agreement.  \\ \hline{}
	Fee & A recurring fee paid by the Client to the Contractor for
	      rendering the services prescribed by the Agreement for the duration of the
	      Service Period which includes the Energy Fee, the Renovation Fee and the
	      Operation and Maintenance Fee, along with any taxes due (such as VAT) in
	      delivering the service and the amount due for domestic hot water consumption. \\ \hline{}
	Heat Supply & Supply of thermal energy to the Building or the Apartment for the needs of space heating or domestic hot water preparation. \\ \hline{}
	Heating Season & Period in the year when the Contractor shall ensure
			 operation of the heating system (heat supply) in the Apartments of the Building
			 and guarantees the Comfort Standards set out in the Agreement. \\ \hline{}
	Invoice & An invoice issued by the Manager on behalf of the Contractor,
		  the Contractor alone or a duly authorized person of the Contractor to the
		  Apartment Owner (or duly authorized representative of the Apartment owner) for
		  the Services received during the Settlement Period and for other payments due
		  to the Contractor arising out of the Agreement. Invoices shall be issued in
		  full compliance with all applicable statutory requirements under Latvian law. \\ \hline{}
	LABEEF & means the Latvian Baltic Energy Efficiency Facility Jsc.,
		 operating as a joint stock company duly registered in the Commercial
		 register of Latvia under corporate No. 40103960646 \\ \hline{}
	Latent Condition(s) & Latent Conditions are physical conditions of the
			      Building or its near surroundings, including artificial things or dangerous or
			      toxic materials or substances that require specific removal not having been
			      made known to the Contractor at the outset of this Agreement, but excluding
			      weather conditions or physical conditions which are a consequence of weather
			      conditions, which differ materially from the physical conditions which the
			      Contractor anticipated or which should reasonably have been anticipated by a
	   		      competent Contractor exercising good industry practice at the time of the
			      Contractor’s signature of the Agreement and which would affect the completion
			      of the Renovation Works if the Contractor had inspected:
			      \begin{itemize}
			      		\item all information made available in writing by the Client to the Contractor for the purpose of contemplating entering into the Agreement;
					\item all information relevant to the
					      risks, contingencies and other circumstances having an effect on the proposed
					      Agreement and obtainable by the making of reasonable enquiries; and
					\item the Building and its surroundings.
			      \end{itemize} \\ \hline{}
	Logger & Equipment for measurement, verification and record keeping of thermal energy. \\ \hline{}
	Manager & An individual or a legal entity, who in line with the
		  applicable provisions of the Latvian Law on Management of Residential Housing
		  and based on a management agreement, carries out managerial activities assigned
		  by the Client in respect of the Building as well as the duties established by
		  the Agreement. The management agreement pursuant to which the Manager renders
		  its services shall be attached to the current Agreement for reference purposes. \\ \hline{}
	Measurement and Verification & The process of determining energy savings using LABEEF Financial and Technical Rules and Guidelines for Energy Efficiency Measures \\ \hline{}
	Operational and Maintenance Manual & A manual indicating:
					     \begin{itemize}
							\item the maintenance schedule for the Renovation Works implemented under this agreement
							\item the operational activities covered by the Agreement
					     \end{itemize} \\ \hline{}
	Parties & The Contractor and the Client collectively. \\ \hline{}
	Party & The Contractor and the Client each individually. \\ \hline{}
	Payment Period & A 12{-}month period between 1st July of each year and
			 30th June of the following year. The first payment period is set from the day
			 of commencing provision of the Services until 30th of June of the respective year. \\ \hline{}
	Progressive Compensation Scheme & A scheme of calculation used to
					  establish compensation payable to the Contractor for termination of the
					  Agreement before expiry of the Service Period. \\ \hline{}
	Project Development costs & The cost incurred for the development of a
				    building renovation projects, including but not limited to the costs for energy
				    audits, civil engineering appraisals, project technical design, project
				    management and coordination, construction permits and the organisation of
				    project financing. \\ \hline{}
	Proper Functioning of the Facilities & The Proper Functioning of the
					       Facilities is the functioning of the Facilities in such a manner as to ensure
					       the achievement of their full functionalities and efficiency and includes all
					       necessary actions undertaken by and at the expense of the Contractor including
					       the transportation of materials/equipment, delivery, installation, replacement,
					       clean up after works, labour and any other related activities for the
					       fulfilment of the guaranteed Energy Savings and Quality Standards. \\ \hline{}
	Reference Period & Period of time (calendar year of the years 20[X],
			   20[X] and 20[X]) used by the Parties as a reference for settlement of accounts. \\ \hline{}
	Regulator & The Public Utilities Commission or another applicable
		    authority established in the laws and regulations effective in Latvia which
		    approves tariffs for trading thermal energy in the respective local government
		    where the Building is situated. \\ \hline{}
	Renovation Works & Activities referred in the Agreement resulting in
			   achievement of verifiable and measurable or estimable energy savings.
			   Activities involve engineering, procurement, supply, installation, start{-}up and
			   commissioning for the renovation of the building. All activities are
			   implemented by the Contractor based on the provisions of the Agreement. \\ \hline{}
	Service Period & The period during which the Contractor is obliged to
			 provide Services to the Client under this Agreement. The Service Period shall
			 be considered to start to run automatically after the expiry of the
			 Construction Period and without the need for any additional notifications to
			 that effect. The Contractor may postpone the date for starting to render the
			 Services by extending the end date by the same period as that for which the
			 start date is postponed, if written consent of the Client is received. The
			 commencement of the Service Period shall be considered automatically postponed
			 and extended with the period of the delay in case due to a default or
			 negligence of the Client or any force majeure event the Contractor is not
			 furnished with all due documents and/or access to the Building and/or due to
			 Force Majeure events the Contractor could not execute his contractual
			 obligations stipulated hereinafter. \\ \hline{}
	Services & The Renovation Works, Energy Supply and operation and
		   maintenance of the Facilities performed by the Contractor under the
	           present Agreement. \\ \hline{}
	Settlement Period & The period of one calendar year starting to run as
			    of the date of commencement of the Service Period and recurring on an annual
			    basis after the expiry of which the Client shall settle accounts for the Services. \\ \hline{}
	Statement & A document signed between by the Parties to evidence
		    various parameters present at the Building as recorded at the time of
		    execution of such document. \\ \hline{}
	VAT & The value added tax payable in accordance with laws and regulations effective in Latvia and provisions of the Agreement. \\ \hline{}
\end{longtabu}
\end{center}

Unless the context otherwise requires, as used in this Agreement, the singular
number includes the plural and the plural number may include the singular. The
use of any gender shall be applicable to all genders. Unless otherwise
specified, references to Articles, Sections or subsections are to the Articles,
Sections and subsections in this Agreement. Unless the context otherwise
requires, the term “including” shall mean “including, without limitation”.
