{{template "preamble.tex"}} % chktex 18
\begin{document}

\begin{center}
	\begin{tabu}{|X[2]|X|}\tabucline{}
		Contract number: {{.Contract.ID}} & Date: {{index .Contract.Fields "date"}} \\\tabucline{} %chktex 26
	\end{tabu}
\end{center}

\section{ДОГОВОР С ГАРАНТИРАН РЕЗУЛТАТ}

\textbf{Клиент}:

\begin{center}
	\begin{tabu}{|X|X[2]|}\tabucline{}
		Име & {{.Contract.Fields.client_name}} \iffalse input fields.client_name value="{{.Contract.Fields.client_name}}" \fi \\\tabucline{}
		ЕИК / ЕГН & {{.Contract.Fields.client_id}} \iffalse input fields.client_id value="{{.Contract.Fields.client_id}}" \fi \\\tabucline{}
		Адрес & {{.Contract.Fields.client_address}} \iffalse input fields.client_address value="{{.Contract.Fields.client_address}}" \fi \\\tabucline{}
	\end{tabu}
\end{center}

\textbf{Изпълнител}:

\begin{center}
	\begin{tabu}{|X|X[2]|}\tabucline{}
		Име & {{.ESCo.Name}} \\\tabucline{}
		ЕИК & {{.ESCo.VAT}} \\\tabucline{}
		Адрес & {{.LEAR.Name}} \\\tabucline{}
    Упълномощено лице & {{index .Contract.Fields "legal-representative"}} \\\tabucline{}
	\end{tabu}
\end{center}

Сключиха настоящия договор с гарантиран резултат.

\section{SPECIAL CONDITIONS}
\subsection{SUBJECT}
\begin{enumerate}
\item The Client shall assign, and the Contractor shall accept to
  implement for the multifamily residential building, located at the
  address: {{.Asset.Address}}, cadastre identifier:
  {{.Asset.Cadastre}} the following activities:
  \begin{enumerate}[label=\arabic*.]
  \item Implementation (design and implementation of construction and
    installation works) of energy-saving measures in compliance with
    the report on implemented energy efficiency audit, Annex 1 {–}
    Report and Summary on Building EE Audit (see Annex 1) to this
    contract within scope, under Annex 2 {–} Scope of the measures and
    BOQ (see art. (1) and (2) ) to this contract;
  \item Servicing and maintenance of the implemented energy-saving
    measures for the entire period of the contract and monitoring of
    the energy-saving, for the purpose of accounting the
    energy-savings and achievement of the guaranteed result.
  \end{enumerate}
\item The Contractor is obliged to implement all ESM, in consequence
  of which, the Building shall have a specific energy consumption,
  which shall cover the requirements for energy consumption class
  “[●]”.
\item The energy-savings and achievement of the guaranteed result
  shall be accounted, according to the Method of guaranteed result
  evaluation, Annex 4 {–} Method of guaranteed result evaluation (see
  Annex 4). The Method is developed by the Contractor.
\item The detailed scope of the repair works and related to them
  measures are described in Annex 2 {–} Scope of the measures and BOQ
  (see art. (1) and (2) ) to the contract.
\end{enumerate}

\subsection{GUARANTEED RESULT}
\begin{enumerate}
\item The Parties on the contract shall negotiate the following
  numeric values of BAEC, GAEC and their respective GAES and the
  ecological equivalent of the saved energy:
  \begin{enumerate}
  \item BAEC: [●] kWh/m2, including: (а) thermal energy {-} [●] kWh/year
    and (b) electric energy {-} [●] kWh/year
  \item GAEC: [●] kWh/m2 and [●] kWh/year, including thermal energy -
    [●] kWh/year, electric energy {-} [●] kWh/year,
  \item GAES: [●] kWh/year, including thermal energy {-} [●] kWh/year,
    electric energy {-} [●] kWh/year,
  \item The ecological equivalent of GAES of the Building: [●] tons of
    carbon dioxide/year.
  \item Price of thermal energy by the date of signing the contract
    [●].
  \item Price of electric energy by the date of signing the contract
    [●]. When accounting the VAGES and VAAEC for the entire period of
    the contract, shall be applied to the prices of the energy
    resources under art. (5) and (6) (see Annex 4).
  \end{enumerate}

\item The numeric values of the energy consumption, mentioned in
  art. 186, are determined pursuant to the report on implemented
  energy audit, and the information provided by the Client, as well as
  in conformity with the condition of the Building construction
  outdoor elements, features of the building installation, operation,
  number of occupants and installed energy consumers and the data
  collected by the Contractor during the Building audit, in
  environmental factors specific for Climatic zone No. [●], according
  to Regulation No. E{-}RD{-}04{-}2/22.01.2016 on the energy consumption
  indicators and the energy features of the Buildings.
\item The Contractor, for the monitoring period, shall guarantee the
  comfort standards, described in Annex 3 – Comfort Standards (see
  Annex 3).
\item The Contractor, for the monitoring period, shall implement
  servicing and maintenance of the measures in compliance with the
  provisions, described in detail in Annex 5 {-} Operation and
  Maintenance Manual (see Annex 5).
\end{enumerate}

\subsection{СРОК НА ДОГОВОРА}
\begin{enumerate}
\item This contract enters in force from the date it is being signed
  by the Parties. The term for implementation of the Contract is [●]
  years /months/ and includes the time for execution of Stage 1 and
  Stage 2 below.
\item Stage 1 shall start from the signing of this contract and
  include the time necessary for the design of the measures and the
  construction period and finishes upon commissioning of the measures.
  \begin{enumerate}
  \item The construction period is [●] months.
  \item The term for implementation of Stage 1 is [●] months.
  \end{enumerate}
\item Stage 2 starts from the date of commissioning and includes the
  monitoring period. The monitoring period is [●]
\end{enumerate}

\subsection{PRICE}
\begin{enumerate}
\item The Client shall pay to the Contractor a price for the
  implementation of ESM, a fee for servicing and maintenance, and a
  price for monitoring for the entire period of the Contract, as
  follows:
  \begin{enumerate}
  \item Price for implementation of ESM {-} [●] BGN, VAT excluded, and
    [●] BGN, VAT included. On the price for the performance of ESM
    shall be calculated interest in line with Annex 7 {-} Amortisation
    plan and rules of determination of the sums due by every owner of
    individual apartment (see 1.1 and 1.2)
  \item Price for servicing and maintenance {-} [●] BGN, VAT excluded,
    and [●] BGN, VAT included, due every month for every month, as
    from commissioning until the expiry of the contract term.
  \item Price for monitoring {-} [●] BGN, VAT excluded, and [●] BGN,
    VAT included, due monthly for every month, as from commissioning
    until the expiry of the contract term.
  \item The prices under subart. (ii) and (iii) are subject of
    annual indexation under Annex 8 {-} Rules of indexation of the
    price for servicing and maintenance, and the price for monitoring
    (see art. (4) and (5) ).
  \end{enumerate}
\item The sums under art. 1 subart. (ii) and (iii) shall be
  paid within {{.Contract.Fields.invoiced_days}} days after issuing of the respective invoices.
\item The specific distribution of the obligations of the individual
  owners in the Building and its mode of calculation set out in Annex
  7 {-} Amortisation plan and rules of determination of the sums due
  by every owner of individual apartment (see art.(1) ).
\end{enumerate}

\begin{center}
  \begin{tabu}{|X|X|X|X|}\tabucline{}\rowfont[c]\bfseries
    {{with .Contract.Tables.summary}} % chktex 26
    {{.Columns | column}} \\\tabucline{} {{range .Rows}} % chktex 26
    {{.|row}} \\\tabucline{} {{end}} \bfseries {{total .}}
    \\\tabucline{} % chktex 26
    {{end}}
  \end{tabu}
\end{center}

\subsection{OTHER PROVISIONS}
\begin{enumerate}
\item This contract shall include the General terms and conditions {-}
  Annex 11 {-} General terms and conditions (see 1.1)., the specific
  terms and the Annexes to the specific terms.
\item The Client grants its explicit consent to the Contractor to
  transfer and/or assign for collection to a third person all
  receivables, arising from this contract, or a part of them.
\item An integral part of this contract are the following Annexes,
  signed by the Client, by affixing his signature below, the Client
  shall declare that he has also received a copy of the Annexes,
  including the general terms and conditions:
  \begin{enumerate}
  \item Annex 1 {-} Report and Summary on Building EE Audit;
  \item Annex 2 {-} Scope of the measures and BOQ;
  \item Annex 3 {-} Comfort Standards;
  \item Annex 4 {-} Method of guaranteed result evaluation;
  \item Annex 5 {-} Operation and Maintenance Manual;
  \item Annex 6 {-} Rules of determination of the balance payment
    after measuring and evaluation of the result;
  \item Annex 7 {-} Amortisation plan and rules of determination of
    the sums due by every owner of individual apartment;
  \item Annex 8 {-} Rules of indexation of the price for servicing and
    maintenance, and the price for monitoring;
  \item Annex 9 {-} Determination of the contact persons under this
    contract;
  \item Annex 10 {-} Minutes of Condominium General Meetings regarding
    decisions on conclusion and implementation of this contract, as
    well as all other minutes of decisions under this contract,
    including such held after its signing;
  \item Annex 11 {-} General terms and conditions.
  \end{enumerate}
\end{enumerate}

\vspace{2cm}
{{template "sign.tex"}} % chktex 18

{{template "annex1.tex" .}} % chktex 18
{{template "sign.tex"}} % chktex 18

%% TODO Fix when template is provided
%%template "annex2.tex" .}} % chktex 18 chktex 26
{{template "sign.tex"}} % chktex 18

{{template "annex3.tex" .}} % chktex 18 chktex 26
{{template "sign.tex"}} % chktex 18

{{template "annex4.tex" .}} % chktex 18 chktex 26
{{template "sign.tex"}} % chktex 18

{{template "annex5.tex" .Contract.Tables}} % chktex 18 chktex 26
{{template "sign.tex"}} % chktex 18

{{template "annex6.tex" .}} % chktex 18 chktex 26
{{template "sign.tex"}} % chktex 18

{{template "annex7.tex" .}} % chktex 18 chktex 26
{{template "sign.tex"}} % chktex 18

{{template "annex8.tex" .}} % chktex 18 chktex 26
{{template "sign.tex"}} % chktex 18

{{template "annex9.tex" .Contract.Fields}} % chktex 18 chktex 26
{{template "sign.tex"}} % chktex 18

\pagebreak
\section{Annex 10 {-} Minutes of Condominium General Meetings regarding decisions on conclusion and implementation of this contract, as well as all other minutes of decisions under this contract, including such held after its signing}

Shall be applied the minutes of the owners’ general meetings in reference to the renovation of the Building and conclusion of this contract, payment of the remuneration due to the Contractor, as well as comments of the owners on other essential terms of the contract, authorisation of the Manager to carry out certain activities, and others. The decisions shall be taken in compliance with all rules of the Condominium ownership management act and unanimously by all owners. The minutes have to have notarized signature.

\vspace{2cm}
{{read .Markdown}} % chktex 26
{{template "en_sign.tex"}} % chktex 18
\FloatBarrier{}\mbox{}\vfill\pagebreak % make sure no floats (e.g. images) go past here.

{{template "terms.tex"}} % chktex 18
{{template "sign.tex"}} % chktex 18
\end{document}
